\vspace{-2.2cm}Multilevel selection in causal models: the multiplicative nature of evolutionary and probabilistic selection processes as the general driver for the irreversibility emergence of cooperation and specialization (Summary paper).\footnote{Add stable link to this summary file}

### 2022-02-15 article.tex
Pequeñas modificaciones

%opening
\title{\vspace{-2.2cm}Multilevel selection in causal models: the multiplicative nature of evolutionary and probabilistic selection processes as the general driver for the emergence of cooperation and specialization.\footnote{\url{https://github.com/glandfried/transitions/releases/download/doc.0.1.0/landfried-trans\en{itions}\es{iciones}.pdf} } }
\author{Gustavo Landfried$^1$}
\affil{\small 1. Universidad de Buenos Aires. Facultad de Ciencias Exactas y Naturales. Departamento de Computaci\'on. Buenos Aires, Argentina}
\affil{\en{Mail}\es{Correo:} \url{glandfried@dc.uba.ar}}

>>>>

%opening
\title{\vspace{-2.2cm}Multilevel selection in causal models: the multiplicative nature of evolutionary and probabilistic selection processes as the general driver for the irreversibility emergence of cooperation and specialization. \footnote{\url{https://github.com/glandfried/transitions/releases/download/doc.0.1.0/landfried-trans\en{itions}\es{iciones}.pdf} } }
\author{Gustavo Landfried$^1$}
\affil{\small 1. Universidad de Buenos Aires. Facultad de Ciencias Exactas y Naturales. Departamento de Computaci\'on. Buenos Aires, Argentina}
\affil{\en{Mail}\es{Correo:} \url{glandfried@dc.uba.ar}}

### 2022-02-15 summary.tex
Pequeñas modificaciones

%opening
\title{\vspace{-2.2cm}Multilevel selection in causal models: the multiplicative nature of evolutionary and probabilistic selection processes as the general driver for the emergence of cooperation and specialization (Summary paper).\footnote{Add stable link to this summary file} }
\author{Gustavo Landfried$^1$}
\affil{\small 1. Universidad de Buenos Aires. Facultad de Ciencias Exactas y Naturales. Departamento de Computaci\'on. Buenos Aires, Argentina}
\affil{\en{Mail}\es{Correo:} \url{glandfried@dc.uba.ar}}

>>>>

%opening
\title{\vspace{-2.2cm}Multilevel selection in causal models: the multiplicative nature of evolutionary and probabilistic selection processes as the general driver for the irreversibility emergence of cooperation and specialization (Summary paper).\footnote{Add stable link to this summary file} }
\author{Gustavo Landfried$^1$}
\affil{\small 1. Universidad de Buenos Aires. Facultad de Ciencias Exactas y Naturales. Departamento de Computaci\'on. Buenos Aires, Argentina}
\affil{\en{Mail}\es{Correo:} \url{glandfried@dc.uba.ar}}
